A novel distributed nature-inspired algorithm for solving optimization problems\thanks{Supported by TECNOLÓGICO NACIONAL DE MÉXICO (TecNM).}

### 2021-09-28 paper.tex
Work in progress
New Experiments Chart border

Where:
\begin{description}  % When enumerating with description, bullet alternatives: cdot, bullet, ast
    \item[$\bullet$ F] is the gravitational force acting between two objects
    \item[$\bullet$ m1 and m2] are the masses of the objects
    \item[$\bullet$ r]	is the distance between the centers of their masses
    \item[$\bullet$ G]	is the gravitational constant: 6.67430(15)×10−11 m3⋅kg−1⋅s−2
\end{description}

@@

For each experiment, we ran 60 independent executions per algorithm and
recorded the following results: Last Generation, Total Evaluations, Time
(seconds), Evaluations/second. The labels used on the table header are the
following:

@@

\begin{figure}
    \includegraphics[width=\textwidth]{img/fig6_experiment01_chart.pdf}
    \caption{Box and Whisker chart for the Experiment 1: OneMax DEAP versus Life-Cycle (10 processes).} \label{fig6}
    \end{figure}

@@

\begin{figure}
    \includegraphics[width=\textwidth]{img/fig7_experiment02_chart.pdf}
    \caption{Box and Whisker chart for the Experiment 2: Life-Cycle Tournament selection (10 versus 5 processes).} \label{fig7}
    \end{figure}

@@

\begin{figure}
    \includegraphics[width=\textwidth]{img/fig8_experiment03_chart.pdf}
    \caption{Box and Whisker chart for the Experiment 3: Life-Cycle Tournament (6 proc. Death x2, versus 5 proc. w/115 goal).} \label{fig8}
    \end{figure}

@@

\begin{figure}
    \includegraphics[width=\textwidth]{img/fig9_experiment4_chart.pdf}
    \caption{Box and Whisker chart for the Experiment 4: OneMax DEAP versus Life-Cycle Tournament (5 proc. w/125 goal).} \label{fig9}
    \end{figure}

>>>>

Where:
\begin{description}  % When enumerating with description, bullet alternatives: cdot, bullet, ast
    \item[$\bullet$ F] is the gravitational force acting between two objects.
    \item[$\bullet$ m1 and m2] are the masses of the objects.
    \item[$\bullet$ r]	is the distance between the centers of their masses.
    \item[$\bullet$ G]	is the gravitational constant: 6.67430(15)×10−11 m3⋅kg−1⋅s−2.
\end{description}

@@

For each experiment, we ran 60 independent executions per algorithm and
recorded the following results: Last Generation, Total Evaluations, Time
(seconds), Evaluations/second. The labels used on the header of the results of
our summarized experiments tables are the following:

@@

\begin{figure}
    \fbox{\includegraphics[width=\textwidth]{img/fig6_experiment01_chart.pdf}}
    \caption{Box and Whisker chart for the Experiment 1: OneMax DEAP versus Life-Cycle (10 processes).} \label{fig6}
    \end{figure}

@@

\begin{figure}
    \fbox{\includegraphics[width=\textwidth]{img/fig7_experiment02_chart.pdf}}
    \caption{Box and Whisker chart for the Experiment 2: Life-Cycle Tournament selection (10 versus 5 processes).} \label{fig7}
    \end{figure}

@@

\begin{figure}
    \fbox{\includegraphics[width=\textwidth]{img/fig8_experiment03_chart.pdf}}
    \caption{Box and Whisker chart for the Experiment 3: Life-Cycle Tournament (6 proc. Death x2, versus 5 proc. w/115 goal).} \label{fig8}
    \end{figure}

@@

\begin{figure}
    \fbox{\includegraphics[width=\textwidth]{img/fig9_experiment4_chart.pdf}}
    \caption{Box and Whisker chart for the Experiment 4: OneMax DEAP versus Life-Cycle Tournament (5 proc. w/125 goal).} \label{fig9}
    \end{figure}
